Thesis Draft

### 2015-09-12 main.tex
etimology

In this thesis usage of discarded materials in the process of art making and artwork itself is explored. How it is used by the artist? Is there any differences with the original items? (In other words using discarded materials or trash has specific (or special) meaning? What are the importance of it?) This is a work to explore the re-usage of trash in artworks. (place or the role in the art practice.)

@@

\subsubsection{Types of trashes}

@@

\subsection{What might be meaning of using trash in the artworks? Questioning trash in the context of art}
\begin{itemize}
\item Some works try to raise awareness the problem of trash. (its threat to environment and nature.)
\item Some of them reflect people's lifestyle especially throw away culture. mirroring of current lifestyle.
\item Try to find new combination, meaning from the discarded material that are useless anymore and reached end in the specific lifestyle. to explore new approach, new way. subvert peoples ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
\item Using discarded item to represent other discarded things by the ruling ideology or approach. For example trash can be used to represent refugees. The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential. In other words refugees have potential but we see them as a players that will change our current system. Therefore it can be said that willing to transform trash to treasure is to requires change of current lifestyle. Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
\item One way is to not producing trash. zero trash philosophy. The other one is to transform trash into something else.
\item How does it feel that collecting and working on objects that are generally discarded? (experiencing out of common practice, it is open to new explorations...)
\item Instead of a world that produce trash, how could it be a world created from trash?
\end{itemize}

@@

>>>>

In this thesis usage of discarded materials in the process of art making and artwork itself is explored (or researched). How it is used by the artist? Is there any differences with the original items? (In other words using discarded materials or trash has specific (or special) meaning? What are the importance of it?) This is a work to explore the re-usage of trash in artworks. (place or the role in the art practice.)

@@

It can be thought that when the complexity of trashed increased to effort to repair, reuse and recycle is increase. Therefore for ones that has no such complex tools it is becoming harder to reuse them. In other words objects become more complex their re-usage becomes less likely.

\subsubsection{Types of trashes}
Different production process generates different types of trash.

@@

\subsection{What might be meaning of using trash in the artworks? Questioning trash in the context of art}
\begin{itemize}
\item Some works try to raise awareness the problem of trash. (its threat to environment and nature.)
\item Some of them reflect people's lifestyle especially throw away culture. mirroring of current lifestyle.
\item Try to find new combination, meaning from the discarded material that are useless anymore and reached end in the specific lifestyle. to explore new approach, new way. subvert peoples ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
\item Using discarded item to represent other discarded things by the ruling ideology or approach. For example trash can be used to represent refugees. The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential. In other words refugees have potential but we see them as a players that will change our current system. Therefore it can be said that willing to transform trash to treasure is to requires change of current lifestyle. Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
\item One way is to not producing trash. zero trash philosophy. The other one is to transform trash into something else.
\item How does it feel that collecting and working on objects that are generally discarded? (experiencing out of common practice, it is open to new explorations...)
\item Instead of a world that produce trash, how could it be a world created from trash?
\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community. It also signifies that trash still has a good quality to used with new materials. Creating composite products from new and reused items. Using valuable thing with invaluable thing. It become more valuable or less valuable. depends on the idea.
\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. trash portraits, sculptures.)
\end{itemize}

\section{Etymology}
In this topic there are widely used keywords, it is important to clarify them.

The concept of reuse is when a product that is newly purchased is put to another use after the first use is completed. In layman terms an item is reused for the same purpose or another purpose. Reuse is considered to have a massive impact on environment as an item which would have been thrown out, is being given a new purpose. It also eliminates the need to buy another new product, contributing to reduce. The concept of reuse includes anything object that can be used again maybe for a short term as well as long term. An example of reusing would be carrying a cloth bag while going shopping. Since the cloth bag can be used more than once, a person would not have to keep purchasing new paper or plastic bags, hence reducing amount of waste. Reusing can also include using older materials for decorating or other purposes. Plastic bottles can be reused in order to cut the top of and create pen holders. Milk crates can be made into storage compartments. Even donating is a form of re-use, where another person can make use of items that are no longer of use to the person donating them. Salvation Army, churches and various other places hold donation centers where people donate old clothes, shoes, toys, etc that are in turn given to less fortunate people.

Recycling is processing of used materials (waste) into new products to prevent waste of potentially useful materials. The waste is converted into raw materials for a new product. Recycling helps reduce the consumption of fresh raw materials, energy usage, air pollution (from incineration) and water pollution (from landfilling) by reducing the need for "conventional" waste disposal, and lower greenhouse gas emissions as compared to virgin production. Material such as glass, metal, plastic, paper and cloth can be reprocessed and used to create brand new products. Plastic bottles are melted to create new plastic bottles. Even electronics, such as computers, cell phones, TVs, etc can be taken apart and the components can be upgraded and used for new electronics. A set back of recycling is that it has to be sorted and cleaned before it can be processed into new material. This can add extra costs on the part of the company. However, many companies are still turning to the concept of recycling as in the long run it is cheaper compared to purchasing new raw materials every time. In order to make it easier for recycling, people are usually asked separate plastic, glass and paper from other waste.

The root of words waste, garbage, trash, rubbish, scrap, junk, refuse.

Waste "squander, spend or consume uselessly". Garbage giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food. Garbology "study of waste as a social science". "In modern American usage garbage is generally restricted to mean kitchen and vegetable wastes".

@@

\section{Artwork}
\subsection{Why (package) paper?}
